### 2019-02-04 thesis_report/conclusion.tex
Majorana's -> Majoranas
updated methods, spell check conclusions

\comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
The current used quasiclassical analogy, applied in the most lenient form, is not able to explain the increased gap of a zigzag system.
Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or, if the arising phenomena are due to other mechanisms.
In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
Further study should be devoted to isolating the working principle behind the improvements of the zigzag geometry.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
In the model used, we omit several physical effects, such as, disorder, electrostatics, the orbital effect, etc.
Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
We note that slight modifications to the geometry, for example to ease measurement, should not have large implications on the physics.
Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake like and offset sinosoid modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majorana's would be an interesting continuation.

>>>>

\comment{With the current quasiclassical analogy, we are not able to explain the improvements of zigzag.}
The current used quasiclassical analogy, applied in the most lenient form, is not able to explain the increased gap of a zigzag system.
Furthermore, numerical simulation points out that the optimal geometry does not always coincide with the minimal trajectory length.
It is therefore unsure whether the improvement of the gap can be fully attributed to the elimination of long trajectories, or if the arising phenomena are due to other mechanisms.
In any case, the improvements are stable under a wide range of parameters, and the topological gap varies gradually as a function of geometry, indicating the effect is not merely coincidental.
Further study should be devoted to isolating the working principle behind the improvements of the zigzag geometry.

\comment{Extensions: we omit several physical effects, disorder, electrostatics, etc.}
In the model used, we omit several physical effects, such as disorder, electrostatics, the orbital effect, etc.
Apart from experimental verification, further study is required to see whether the conclusions of this model are valid.

\comment{Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.}
Current fabrication techniques seem compatible with the proposed geometry, and experimental verification should point out whether it holds up to its promise.
We note that slight modifications to the geometry, for example, to ease measurement, should not have large implications on the physics.
Currently, experimental groups have already fabricated zigzag devices (e.g. the image on the cover of this thesis), and measurements are underway.

\comment{It would be interesting to study what geometry creates an optimal environment for Majorana modes to exist.}
We have studied sawtooth, snake-like and offset sinusoidal modulation of the semiconductor region, but perhaps a more exotic shape will be optimal.
A study optimizing the geometry for supporting Majoranas would be an interesting continuation.

### 2019-02-04 thesis_report/methods.tex
Changed QC image
Added Bass corrections
updated methods, spell check conclusions

% -*- root: ./report.tex -*-
\chapter{Methods}

\section{Physical picture}
	\comment{We consider a two-dimensional system with zigzag.}
	We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
	We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
	Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
	Both parts have a kinetic term and chemical potential $\mu$ (counted from the bottom spin-orbit band). 
	For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\columnwidth]{images/zigzag.pdf}
	\caption{Setups. Figure of a straight and zigzag system, including trajectories.
	\label{fig:setup}}
	\end{figure}

@@

\subsection{Symmetry class of system}
	\comment{The symmetry class of the system is D.}
	The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}, unless the additional symmetries are broken due to for example a difference in superconducting gap magnitude between the two superconductors.
	Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.

@@

	\comment{We use kwant to make systems and extract the eigenstates}
	We use a tight-binding model, implemented using Kwant, to simulate various properties of the system.
	The model consists of a two-dimensional square lattice of sites.
	Each site has two orbitals: spin and electron-hole.
	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulate an imperfect NS interface.
	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.

	\comment{The model hamiltonian is converted into the tight binding form by substitution}
	In order to turn the set of Hamiltonians, Eqs.\eqref{eq:hamiltonian_n} and \eqref{eq:hamiltonian_s} into a tight binding model, we write the equations into differential form by substituting $k_\alpha \rightarrow - i \partial_\alpha$, $\alpha \in \left\{ x, y \right\}$, and thereafter discretize on a rectangular grid.
	In practice, this is implemented using the Kwant discretizer module.

@@

\comment{We propose a method to verify that elimination of long trajectories is responsible for the increased topological gap in a zigzag system.}
\section{Quasiclassical estimation of the topological gap}
	\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
	In order to establish that the elimination of long trajectories is the driving mechanism behind the order of magnitude gap improvement, we use an analytical approach.
	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag.
	The spectrum of the zigzag segment we define as the spectrum of an infinite ribbon SNS junction with tilted-magnetic field. 
	The finite length of the segment is modeled by not including momenta corresponding to long trajectories when taking the minimum over the spectrum.

	\comment{The spectrum is derived using a scattering matrix, and we consider multiple ways to eliminate long trajectory momenta.}

	Estimating the gap is a two-step process: derivation of the Andreev spectrum, and taking the minimum energy over a particular set of allowed momenta.
	The first is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
	The second step is mostly trivial, but the difficulty lies with identifying the set of allowed  momenta to take the minimum over.

>>>>

% -*- root: ./report.tex -*-
\chapter{Methods}\label{chap:methods}

\section{Physical picture}\label{sec:physical_picture}
	\comment{We consider a two-dimensional system with zigzag.}
	We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
	We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
	Similar to the conventional straight system \cite{pientka_topological_2017}, a magnetic field $B_x$ is applied, along the x-axis.
	We model the system with a BdG Hamiltonian, Eqs.~\eqref{eq:hamiltonian_n}-~\eqref{eq:hamiltonian_s}  ; the normal part has a linear Rashba spin-orbit coupling term characterized by the spin-orbit strength $\alpha$ , and a Zeeman energy $E_z= mu_B g B_x$.
	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\pm\phi/2$ (the phase difference between the superconductors is $\phi$).
	Both parts have a kinetic term and chemical potential $\mu$ (counted from the bottom spin-orbit band). 
	For the zigzag geometry, we first consider a sawtooth like pattern where $z_y$ is the amplitude, $z_x$ is the period, and $W$ the width of the junction.

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\columnwidth]{images/zigzag.pdf}
	\caption{Figure of a zigzag system.
	$z_x$, $z_y$ and $W$ describe the geometry of the zigzag junction.
	$H_\text{K}$ describes the kinetic part of the Hamiltonian, $H_\text{SOI}$ is the spin-orbit term, $H_\text{Z}$ is the Zeeman coupling, and $H_\Delta$ represents the superconducting term.
	The magnetic field (B) points along the x-axis.
	\label{fig:setup}}
	\end{figure}

@@

\subsection{Symmetry class of system}
	\comment{The symmetry class of the system is D.}
	The non-zigzag system is in the symmetry class BDI \cite{pientka_topological_2017}, unless the additional symmetries are broken due to for example a difference in superconducting gap magnitude between the two superconductors.
	Using the software package Qsymm\cite{varjas_qsymm_2018}, we find that the symmetry class of our system to be D, because we break this chiral/time-reversal symmetry resulting from the mirror symmetric junction.

@@

	\comment{We use kwant to make systems and extract the eigenstates}
	We use a tight-binding model, implemented using Kwant, to simulate various properties of the system.
	The model consists of a two-dimensional square lattice of sites.
	Each site has two orbitals: spin and electron-hole.
	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with an optional potential offset, acting as a barrier to simulate an imperfect NS interface.
	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.

	\comment{The model hamiltonian is converted into the tight binding form by substitution}
	In order to turn the set of Hamiltonians, Eqs.\eqref{eq:hamiltonian_n} and \eqref{eq:hamiltonian_s} into a tight binding model, we write the equations into differential form by substituting $k_\alpha \rightarrow - i \partial_\sigma$, $\sigma \in \left\{ x, y \right\}$, and thereafter discretize on a rectangular grid.
	In practice, this is implemented using the Kwant discretizer module.

@@

\comment{We propose a method to verify that elimination of long trajectories is responsible for the increased topological gap in a zigzag system.}
\section{Quasiclassical estimation of the topological gap}
	\comment{To compute the effect of cutoff consider a single segment of the zigzag and obtain the spectrum analytically (this allows to use translation invariance).}
	To establish that the elimination of long trajectories is indeed the driving mechanism behind the improvement of the gap, we use an analytical model in an effort to isolate the gap-trajectory dependence.
	We estimate the gap of the zigzag system by the minimum energy occuring in the Andreev spectrum of a single (diagonal) segment of zigzag (see Fig.~\ref{fig:zigzag_methods}).
	We define the spectrum of a single zigzag segment by identifying it with the spectrum of an infinite ribbon SNS junction with tilted-magnetic field.
	The finite length of the segment is modeled by not including momenta corresponding to long trajectories when taking the minimum over the spectrum.

	\comment{The spectrum is derived using a scattering matrix, and we consider multiple ways to eliminate long trajectory momenta.}
	Estimating the gap is a two-step process: first, derivation of the Andreev spectrum, and second, taking the absolute minimum of that spectrum over the set of momenta allowed by the specific geometry.
	An analytic expression for the spectrum is derived using scattering matrix formalism and the Andreev bound state condition\cite{beenakker1991universal, sticlet_robustness_2017}.
	For the second step, the difficulty lies with identifying the set of allowed momenta in a particular geometry.

### 2019-02-04 thesis_report/theory.tex
review results.tex
updated methods, spell check conclusions

\chapter{Theoretical Background}
A topological quantum computer uses pairs of Majorana bound states as its unit of computation (qubit).
In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
As this material does not seem to exist on its own, one creates a heterogeneous system.
I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majoranas.

@@

    \subsection{Spin-orbit coupling}
	    An electron moving in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
	    The resulting interaction, coupling the momentum and spin of electron, is known as spin orbit coupling.
	    Spin-orbit coupling can be approximated by adding a Rashba spin orbit coupling term in the Hamiltonian:
	    \begin{equation}
	    H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
	    \end{equation}

\section{Superconducting region}
    The superconductor is responsible for ensuring particle-hole symmetry, as well as providing a `gapped' area in the bandstructure, isolating the zero-energy state.
    Superconductivity is a very complicated phenomenon, so we again provide only the background required for the understanding of this work.

>>>>

\chapter{Theoretical Background}\label{chap:theory}
A topological quantum computer uses pairs of Majorana bound states as its unit of computation (qubit).
In order to host Majorana modes in a system, one needs a material which has properties from a superconducting material, as well as from a semi-conducting material.
As this material does not seem to exist on its own, one creates a heterogeneous system.
I simple terms, this consists of a slab of superconductor and a strip of semiconductor.
By interfacing the two, one creates a region where all the necessary ingredients are present to realize Majoranas.

@@

    \subsection{Spin-orbit coupling}
	    An electron moving in an electric field will experience a small Zeeman field in its inertial frame as a relativistic effect~\cite{petersen_simple_2000}.
	    The resulting interaction, coupling the momentum and spin of electron, is known as spin orbit coupling.
	    Spin-orbit coupling can be approximated by adding a Rashba spin orbit coupling term in the Hamiltonian:
	    \begin{equation}
	    H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
	    \end{equation}
	    Where $\alpha$ is known as the spin-orbit coupling strength.
	    Using this coupling strenght $\alpha$, we can also define the spin-orbit length~\cite{van_weperen_spin-orbit_2015}:
	    \begin{equation}
	    	l_\text{so} = \frac{\hbar^2}{2\meff \alpha}
	    	\label{eq:l_so}
	    \end{equation}
	    In a two-dimensional system, if $l_\text{so}$ is smaller than the length of the system, then spin-orbit interaction will not have a large impact upon the physics.
\section{Superconducting region}
    The superconductor is responsible for ensuring particle-hole symmetry, as well as providing a `gapped' area in the bandstructure, isolating the zero-energy state.
    Superconductivity is a very complicated phenomenon, so we again provide only the background required for the understanding of this work.
